ComparativePlots

### 2018-10-02 ComparativePlots.Rmd
24/9 Update (first manuscript draft, yay!)
Critical Analysis and index add

@@

>>>>

cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#c0d884",
           brewer.pal(n = 9, name = "YlGn")[4:9])

@@

```{r}
Lepidothrix.coeruleocapilla.data <- restricted.data %>% filter(TipLabel == "Lepidothrix_coeruleocapilla")

LC.bioclim4 <- data.frame(
  value = rnorm(1000, mean = Lepidothrix.coeruleocapilla.data$bioclim4, sd = Lepidothrix.coeruleocapilla.data$se.bioclim4))

LC.bioclim4$name <- "bioclim4"

LC.bioclim4 %>% ggplot()+
  geom_density_ridges(aes(x = value/10, y = 0), rel_min_height = 0.005, fill = "#fc8d62")+
  scale_y_discrete(expand = c(0,0))+
  ylab("")+
  xlab("Temperature Seasonality")+

  theme_bw()+

  theme(
        text = element_text(size=18),
        panel.border= element_blank(),
        axis.line.y =element_blank(),
        axis.line.x = element_line(),
        axis.ticks.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=18), 
        legend.title=element_text(size=18, face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 24),
        axis.title.y = element_text(size = 18, hjust = 0.35, margin = margin(r=-10)),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18))
```

```{r}
Lepidothrix.coeruleocapilla.data <- restricted.data %>% filter(TipLabel == "Lepidothrix_coeruleocapilla")

LC.NPP <- data.frame(
  value = rnorm(1000, mean = Lepidothrix.coeruleocapilla.data$NPP, sd = Lepidothrix.coeruleocapilla.data$NPP.se))

LC.NPP$name <- "NPP"

LC.NPP %>% ggplot()+
  geom_density_ridges(aes(x = value/10, y = 0), rel_min_height = 0.005, fill = "#a6d854")+
  scale_y_discrete(expand = c(0,0))+
  scale_x_continuous(limits = c(1910, 2010))+
  ylab("")+
  xlab("NPP")+

  theme_bw()+

  theme(
        text = element_text(size=18),
        panel.border= element_blank(),
        axis.line.y =element_blank(),
        axis.line.x = element_line(),
        axis.ticks.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=18), 
        legend.title=element_text(size=18, face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 24),
        axis.title.y = element_text(size = 18, hjust = 0.35, margin = margin(r=-10)),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18))

LC.NPP <- data.frame(
  value = rnorm(1000, mean = Lepidothrix.coeruleocapilla.data$NPP, sd = Lepidothrix.coeruleocapilla.data$NPP.se))

LC.NPP$name <- "NPP"

LC.NPP %>% ggplot()+
  geom_density_ridges(aes(x = value/10, y = 0), rel_min_height = 0.005, fill = "#a6d854")+
  scale_y_discrete(expand = c(0,0))+
  scale_x_continuous(limits = c(1910, 2010))+
  ylab("")+
  xlab("NPP")+

  theme_bw()+

  theme(
        text = element_text(size=18),
        panel.border= element_blank(),
        axis.line.y =element_blank(),
        axis.line.x = element_line(),
        axis.ticks.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=18), 
        legend.title=element_text(size=18, face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 24),
        axis.title.y = element_text(size = 18, hjust = 0.35, margin = margin(r=-10)),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 18))
```

```{r}
#read nexus
manakin.trees <- read.nexus(file.choose())
#get MCC
manakin.tree <- maxCladeCred(manakin.trees)

manakin.DR <- calculate.log.es(manakin.tree)
```
